Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-05-30 background.tex
2015.05.30 (Vassilis) Changes added based on Hüseyin's comments. Mainly minor re-wording and fixing typos.

Over the past several years, researchers have investigated an extensive
array of heuristic solutions to the topology mismatch problem. 
The purpose of this survey is to gather and organize 
this extensive body of produced knowledge. 
We aspire to assist the reader in better understanding the 
different approaches suggested and to accomplish this, we 
present methods for both structured and unstructured distributed 
overlay networks.
We outline the respective algorithmic aspects and we categorize
the surveyed material so that pros and cons of each method
can become apparent in their context.

@@

For the \emph{overhead} criterion, we evaluate the cost
of computing and communicating peer join, message forwarding, 
and overlay topology maintenance. For instance, the overhead that an algorithm,
which needs global knowledge of the overlay topology, imposes to the system is
greater compared to a protocol that only relies on peers exchanging routing
tables within a a 2-hop radius from each other.
%%VM Reworked definition of overhead and explanatory sentence.
%%

For the \emph{scalability} criterion, we consider system behavior with respect
to the number of participating peers it can reliably support. We characterize
protocols as being lowly, mediumly or highly scalable if the are proven to
effectively support hundreds, tenths of thousands or millions of nodes,
respectively.
%%%VM Reworked definition.
%%

>>>>

Over the past several years, researchers have investigated an extensive
array of heuristic solutions to the topology mismatch problem.
The purpose of this survey is to gather and organize
this extensive body of produced knowledge.
We aspire to assist the reader in better understanding the
different approaches suggested and to accomplish this, we
present methods for unstructured and structured
overlay networks.
We outline the respective algorithmic aspects and we categorize
the surveyed material so that pros and cons of each method
can become apparent in their context.

@@

For the \emph{overhead} criterion, we evaluate the cost
of computing and communicating peer join, message forwarding, 
and overlay topology maintenance. For instance, the overhead that an algorithm,
which needs global knowledge of the overlay topology, imposes to the system is
greater compared to a protocol that only relies on peers exchanging routing
tables within a 2-hop radius from each other.

For the \emph{scalability} criterion, we consider system behavior with respect
to the number of participating peers it can reliably support. We characterize
protocols as being lowly, mediumly or highly scalable if they are proven to
effectively support hundreds, tenths of thousands or millions of nodes,
respectively.

### 2015-05-30 intro.tex
2015.05.30 (Vassilis) Changes added based on Hüseyin's comments. Mainly minor re-wording and fixing typos.

For over a decade, researchers have extensively investigated  
various aspects of the topology mismatch problem.
The main objective of this paper is to offer a comprehensive 
survey of the work carried out in the area
and provide a
taxonomy of the proposed solutions. We point out synergies, as well as
similarities and differences in the published approaches. 
Ultimately, our goal is to help readers sift through 
the voluminous literature, to help them
understand the advantages and disadvantages of each work, and 
to provide them with enough perspective so that 
when the need arises, they are able to
select, amongst the different approaches, the one that is most suitable for
their particular application.
%%
The rest of the paper is organized as follows: 
Section~\ref{section:background} provides background on
overlay architectures including centralized, decentralized-unstructured and
decentralized-structured \p\ systems.
We also formally define the problem of topology mismatch 
and offer the rationale behind our 
evaluation of the techniques discussed in this paper. 
Sections~\ref{section:unstructured} and~\ref{section:structured}
respectively outline the surveyed research efforts 
for decentralized-unstructured and decentralized-structured \p\ systems.
Conclusions can be found in Section~\ref{section:conclusion}.

>>>>

For over a decade, researchers have extensively investigated  
various aspects of the topology mismatch problem.
This research area started to become active after  The mismatch problem is Interest around All interesting work around the topology We omitted centralized Centralized systems are not

The main objective of this paper is to offer a comprehensive 
survey of the work carried out in the area
and provide a
taxonomy of the proposed solutions. We point out synergies, as well as
similarities and differences in the published approaches. 
Ultimately, our goal is to help readers sift through 
the voluminous literature, to help them
understand the advantages and disadvantages of each work, and 
to provide them with enough perspective so that 
when the need arises, they are able to
select, amongst the different approaches, the one that is most suitable for
their particular application.
%%
The rest of the paper is organized as follows: 
Section~\ref{section:background} provides background on
overlay architectures including centralized, decentralized-unstructured and
decentralized-structured \p\ systems.
We also formally define the problem of topology mismatch 
and offer the rationale behind our 
evaluation of the techniques discussed in this paper. 
Work in the area was inspired mostly due to the volatile and fully
distributed nature of the decentrilized overlays so we skip
centralized systems and in Sections~\ref{section:unstructured} and~\ref{section:structured}
we outline the surveyed research efforts
for unstructured and structured \p\ overlays, respectively.
Conclusions can be found in Section~\ref{section:conclusion}.
